Advanced Normalization Tools (ANTS)

### 2009-08-19 Documentation/Tex/ants.tex
tcsh issues
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@99 fd2da0a4-d968-48df-9cb5-d8c496287cbf

\subsection{ANTS Scripts} 
The ANTS/Scripts directory contains (hopefully) user-friendly wrappings of ANTS tools 
that enable higher-level error checking and combinations of basic ANTS functions. 
These scripts are called as \verb sh  ~ \verb antsscriptname.sh ~ and provide usage when 
called from the command line.  For instance, try \verb sh ~ \verb ants.sh .

>>>>

\subsection{ANTS Scripts} 
The ANTS/Scripts directory contains (hopefully) user-friendly
wrappings of ANTS tools that enable higher-level error checking and
combinations of basic ANTS functions.  These scripts are called as
\verb sh ~ \verb antsscriptname.sh ~ and provide usage when called
from the command line.  For instance, try \verb sh ~ \verb ants.sh .
Additionally, if you run ants in tcsh shells, you will need to call it
as follows:
\begin{verbatim}
~/Code/ANTSSourceForgeSVN/bin/ANTS 2 -m PR\[r16slice.nii,r64slice.nii,1,2\]
\end{verbatim}
instead of
\begin{verbatim}
~/Code/ANTSSourceForgeSVN/bin/ANTS 2 -m PR[r16slice.nii,r64slice.nii,1,2]
\end{verbatim}
because tcsh does no interpret the brackets as intended.  Using the
bash shell script interface also avoids this.  The key change involves using the slash to force tcsh to 
interpet the bracket literally.
